\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/intro.tex
minor edits to intro and abstract.

Our goal is to build a framework that enables programmers, who are not
expert in cryptography, to easily program efficient and scalable \mpc
protocols. Since its introduction in 1980s, there has been a long
sequence of work along the same lines. To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server model, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^{T}$ and $x$. Alice has following options.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{gentry}).
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can be either expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
Hence, for better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work. Below we describe the
salient features of \tool.

@@

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and hence, the array accesses need not be compiled
obliviously. Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Our evaluation
shows that the performance of these automatically generated protocols
is comparable
to or better than the custom, specialized protocols developed in the
previous work. Indeed, \tool is the first such cryptographic-cost
aware compiler.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem proves a
forward simluation between the
``ideal'' semantics (the trusted-third party semantics) of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The simulation
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the back-end cryptographic
protocol. We also prove a formal security theorem for our partitioning
scheme.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctnss and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview.

>>>>

Our goal is to build a framework that enables programmers, who are not
experts in cryptography, to easily program efficient and scalable \mpc
protocols. Since its introduction in 1980s, there has been a long
sequence of work along the same lines. To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Say Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server model, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^{T}$ and $x$. Alice has following options.

@@

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed as either a boolean
circuit~(\cite{yao,gmw}) or an arithmetic circuit~(\cite{gentry}).
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can be either expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%
Unfortunately, none of the above frameworks support combinations of
arithmetic and boolean circuits, and using different tools for
different parts of the computation is cumbersome and error-prone.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, a new \mpc framework.
\tool is the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. The generated protocols comprise combinations
of arithmetic and boolean circuits and have performance comparable to
or better than the custom, specialized
protocols from previous work (up to a factor of 19x in our experiments, depending on the functionality) \nc{I added this but I guess we are saying it many times, but might be nice to highlight perf early no?}. Below we describe the
salient features of \tool.

@@

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and hence, the array accesses need not be compiled
obliviously. Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Our evaluation
shows that the performance of these automatically generated protocols
is comparable
to or better than the custom, specialized protocols developed in previous works. Indeed, \tool is the first such cryptographic-cost
aware compiler.

@@

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem proves a
forward simulation between the
``ideal'' semantics (the trusted-third party semantics) of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The simulation
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the back-end cryptographic
protocol (by also invoking our correctness theorem). We also prove a formal security theorem for our partitioning
scheme.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in Section~\ref{sec:ex}. \nc{provided a pointer to sec 2 as well.}

### 2017-10-28 OaklandSubmission/main.tex
minor edits to intro and abstract.

\maketitle
\begin{abstract}
Secure two-party computation (\mpc) allows two mutually distrusting parties to compute any function on their joint inputs, without revealing anything other than the output of the function to one another. While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat. Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning applications); or c) required cryptographers to design hand-crafted protocols for various applications. In this work, we present \tool: a new ``cryptographic-cost aware'' \mpc framework that generates efficient and scalable \mpc protocols from high-level programs that contain absolutely no cryptographic details. Programs in our language are easy-to-write, with lines of code that are comparable to their insecure implementations. Furthermore, the \mpc protocols generated by our framework outperform or match almost all recent works on hand-crafted secure two-party computation protocols (sometimes up to a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

>>>>

\maketitle
\begin{abstract}
Secure two-party computation (\mpc) allows two mutually distrusting parties to compute any function on their joint inputs, without revealing anything other than the output of the function to one another. While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat. Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning applications); or c) required cryptographers to design hand-crafted protocols for various applications. In this work, we present \tool: a new ``cryptographic-cost aware'' \mpc framework that generates efficient and scalable \mpc protocols from high-level programs that contain absolutely no cryptographic details. Programs in our language are easy-to-write, with lines of code that are comparable to their insecure implementations. Furthermore, the \mpc protocols generated by our framework match or outperform almost all recent works that provide hand-crafted \mpc protocols for various complex functionalities (sometimes up to a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle
